 

### 2022-05-13 thesis/results.qmd
Change layout

![Flow diagram for the systematic scoping review in accordance with the PRISMA 2020 Statement [@page2021]](../plots/flow_diagram.png){#fig-flow}

@@

```{r}
#| echo: false
#| label: tbl-reporting
#| tbl-cap: "Percentage of studies that provided details on the different characteristics of oxygen uptake data processing. *only examined within the subgroup of studies using breath-by-breath measurements"
load("../data/reporting.Rda")
t <- purrr::map_dfr(reporting, scales::percent, accuracy = 0.1)

@@

knitr::kable(
  t,
  col.names = c("Metabolic cart", "Preprocessing", "Software", "Processing Strategy", "Reference"),
  align = "r"
)
```

@@

![Data strategies for processing breath-by-breath data in the reviewed literature (n = 88).](../plots/strategies.png){#fig-strategies}

@@

![Total durations of the calculation interval of V̇O~2max~ in the reviewed studies.](../plots/duration_count.png){#fig-duration}

@@

![V̇O~2max~ varies by data processing strategy. Values are expressed relative to the V̇O~2max~ from a 30-second binned average --- the most common strategy as determined by the review. Solid lines display the median, the shaded area marks the interval between 10th and 90th percentile. Using moving average leads to systematically higher V̇O~2max~ values compared to binned time averages. Changing the averaging interval (in seconds or breaths) can lead to median changes in V̇O~2max~ as large as 5%,.](../plots/comparison.png){#fig-comparison}

@@

![Respiratory Rates peak around 60 min^-1^ in the ramp tests. The red segments correspond to the last minute before exhaustion of each individual (n = 72).](../plots/rr.png){#fig-rr}

>>>>

```{r}
#| echo: false
#| fig-cap: "Flow diagram for the systematic scoping review in accordance with the PRISMA 2020 Statement [@page2021]"
#| fig-scap: "Flow diagram for the systematic scoping review"
#| label: fig-flow
#| out-width: '90%'

knitr::include_graphics("../plots/flow_diagram.png")
```

@@

```{r}
#| echo: false
#| label: tbl-reporting
#| tbl-cap: "Percentage of studies that provided details on the different characteristics of oxygen uptake data processing."
load("../data/reporting.Rda")
t <- purrr::map_dfr(reporting, scales::percent, accuracy = 0.1)

@@

kableExtra::kbl(
  t,
  col.names = c("Metabolic cart", "Preprocessing", "Software", "Processing Strategy", "Reference"),
  align = "r",
  booktabs = TRUE
) |>
  kableExtra::footnote(
    general = "*only examined within the subgroup of studies using breath-by-breath measurements",
    general_title = ""
  )
```

@@

```{r}
#| echo: false
#| fig-cap: "Data strategies for processing breath-by-breath data in the reviewed literature (n = 88)."
#| label: fig-strategies
#| out-width: '90%'

knitr::include_graphics("../plots/strategies.png")
```

@@

```{r}
#| echo: false
#| fig-cap: "Total durations of the calculation interval of V̇O~2max~ in the reviewed studies."
#| label: fig-duration
#| out-width: '90%'

knitr::include_graphics("../plots/duration_count.png")
```

@@

```{r}
#| echo: false
#| fig-cap: "V̇O~2max~ varies by data processing strategy. Values are expressed relative to the V̇O~2max~ from a 30-second binned average — the most common strategy as determined by the review. Solid lines display the median, the shaded area marks the interval between 10th and 90th percentile. Using moving average leads to systematically higher V̇O~2max~ values compared to binned time averages. Changing the averaging interval (in seconds or breaths) can lead to median changes in V̇O~2max~ as large as 5%."
#| fig-scap: "Comparison of different data processing strategies"
#| label: fig-comparison
#| out-width: '90%'

knitr::include_graphics("../plots/comparison.png")
```

@@

```{r}
#| echo: false
#| fig-cap: "Respiratory rates peak around 60 min^-1^ in the ramp tests. The red segments correspond to the last minute before exhaustion of each individual (n = 72)."
#| fig-scap: "Respiratory rates during the ramp tests"
#| label: fig-rr
#| out-width: '90%'

knitr::include_graphics("../plots/rr.png")
```

### 2022-05-13 thesis/thesis.qmd
Change layout

---
title: " "
format: pdf
number-sections: true
top-level-division: section
mainfont: Arial
fontsize: 11pt
urlcolor: blue
linkcolor: black
link-citations: yes
bibliography: ../references.bib
csl: '`r here::here("apa.csl")`'
geometry: "left = 4cm, right = 2cm, top = 2cm, bottom = 2cm"
params:
  title: 'Data Processing Strategies to Determine Maximum Oxygen Uptake: A Systematic Scoping Review and Experimental Comparison'
  name: Simon Nolte
  university: German Sport University Cologne
  year: 2022
---

@@

@@

# Bibliography

@@

## Transparent Changes

@@

## Prisma Reporting Checklist

@@

## Blinded abstract example

@@

## Technical Details

### Session info

### Used Packages

```{r}
p_used <- unique(renv::dependencies(path = "../")$Package)
p_inst <- as.data.frame(installed.packages())
out <- p_inst[p_inst$Package %in% p_used, c("Package", "Version")]
rownames(out) <- NULL
out
```

>>>>

---
title: " "
format: 
  pdf:
    include-in-header: 
      text: \usepackage{setspace}
number-sections: true
top-level-division: section
mainfont: Arial
fontsize: 11pt
urlcolor: blue
linkcolor: black
link-citations: yes
bibliography: ../references.bib
csl: '`r here::here("sports-med-new.csl")`'
geometry: "left = 4cm, right = 2cm, top = 2cm, bottom = 2cm"
params:
  title: 'Data Processing Strategies to Determine Maximum Oxygen Uptake: A Systematic Scoping Review and Experimental Comparison'
  name: Simon Nolte
  university: German Sport University Cologne
  year: 2022
---

@@

\onehalfspacing

@@

# References {.unnumbered}

@@

## Transparent Changes {#sec-tchanges}

@@

## Technical Details {#sec-tech}

### Session Info

### Packages

```{r}
#| message: false

p_used <- unique(renv::dependencies(path = "../")$Package)
p_inst <- as.data.frame(installed.packages())
out <- p_inst[p_inst$Package %in% p_used, c("Package", "Version")]
rownames(out) <- NULL
out
```

@@

## Prisma Reporting Checklist {#sec-checklist}

## Blinded Abstract Example {#sec-blindabstract}

@@
